---
title: "Analysis of 'Category clustering and morphological learning'"
author: "John Mansfield, Carmen Saldana, Peter Hurst, Rachel Nordlinger, Sabine Stoll, Balthasar Bickel & Andrew Perfors"
date: "Last build: `r Sys.Date()`"
output:
  html_document: 
    number_sections: true
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(brms)
options(mc.cores = parallel::detectCores())
library(tidyr)
library(HDInterval)
library(ggridges)
library(viridis)
library(viridisLite)
library(ggpubr)
library(forcats)

se <- function(x) sqrt(var(x)/length(x))
pd <- position_dodge(0.8)
'%!in%' <- function(x,y)!('%in%'(x,y))

```


```{r get data, echo=FALSE}
cat.clust.resp <- read.table("catclust-responses-exp2.txt", header=TRUE, sep="\t", quote="")
cat.clust.resp$Cond <- factor(cat.clust.resp$Cond, levels = c("Simple", "Complex", "Random"))
```


NB The experimental conditions are here labelled:

- Simple: perfectly clustered grammar, all values within a feature appear in the same templatic position
- Complex: unclustered, values for the same feature have different postions in the template but their position is - conditioned and thus perfectly predictable
- Random: affixes have no fixed position,each presentation of a word randomly selects affix order

<!-- ## Response time -->

<!-- We pre-registered to exclude participants with mean RT < 4000 -->

```{r rt, echo=FALSE, message=FALSE, warning = FALSE}
#Check relationship of response time to response accuracy.

participants <- cat.clust.resp %>% group_by(Cond, Username) %>% summarise(propCorrect = sum(Result)/68, meanRT=mean(Response.time))

rt_times <- ggplot(participants, aes(meanRT, propCorrect)) + geom_point() + geom_vline(xintercept = 4000, linetype="dashed")
```


```{r exclude, echo=FALSE}
# Exclude those with sub-4000 meanRT.
# Then break the data down into suffix-tests (main data) and stem tests.

quickies <- subset(participants, meanRT<4000)$Username
cat.clust.resp.cln <- subset(cat.clust.resp, !(Username %in% quickies))
cat.clust.resp.suff <- subset(cat.clust.resp.cln, Infl.distract==TRUE)
cat.clust.resp.suff$Infl.distract <- NULL
cat.clust.resp.stem <- subset(cat.clust.resp.cln, Infl.distract==FALSE)
cat.clust.resp.stem$Infl.distract <- NULL
```

# Data visualisation

## Overall accuracy

### All tests

```{r cond_2, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4, fig.width=6}

condition_overall <- cat.clust.resp.suff %>% group_by(Cond, Username) %>% summarise(propCorrect = mean(Result))
mean.prop_overall <- cat.clust.resp.suff %>% group_by(Cond) %>% summarise(propCorrect = mean(Result), se=se(Result))

plot_prop_overall<- ggplot(condition_overall, aes(x = Cond, y = propCorrect, fill= Cond)) + geom_dotplot(binaxis = 'y',stackdir = 'center',aes(color=Cond), dotsize=0.4, alpha=0.4)+labs(y='proportion of correct responses\n', x = '\n')+ geom_errorbar(mapping=aes(ymin=propCorrect-se, ymax=propCorrect+se), size = 0.7, width=.1, alpha=1, data=mean.prop_overall)+geom_point(shape=21,size=2, alpha=1, data=mean.prop_overall, mapping=aes(y=propCorrect, x=Cond), stroke=1)+theme_minimal(base_size = 16)+scale_color_viridis(discrete = TRUE, option = "D")+scale_fill_viridis(discrete = TRUE, option = "D")+theme(legend.position="none")+ylim(0,1)

plot_prop_overall
```

## Only stem tests

```{r cond_2.1, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4, fig.width=6}

condition_overall <- cat.clust.resp.stem %>% group_by(Cond, Username) %>% summarise(propCorrect = mean(Result))
mean.prop_overall <- cat.clust.resp.stem %>% group_by(Cond) %>% summarise(propCorrect = mean(Result), se=se(Result))

plot_prop_overall<- ggplot(condition_overall, aes(x = Cond, y = propCorrect, fill= Cond)) + geom_dotplot(binaxis = 'y',stackdir = 'center',aes(color=Cond), dotsize=0.4, alpha=0.4)+labs(y='proportion of correct responses\n', x = '\n')+ geom_errorbar(mapping=aes(ymin=propCorrect-se, ymax=propCorrect+se), size = 0.7, width=.1, alpha=1, data=mean.prop_overall)+geom_point(shape=21,size=2, alpha=1, data=mean.prop_overall, mapping=aes(y=propCorrect, x=Cond), stroke=1)+theme_minimal(base_size = 16)+scale_color_viridis(discrete = TRUE, option = "D")+scale_fill_viridis(discrete = TRUE, option = "D")+theme(legend.position="none")+ylim(0,1)

plot_prop_overall
```


## Accuracy by block

```{r blocks_3, echo=FALSE, message=FALSE, warning = FALSE}
cat.clust.resp.suff.seen<-subset(cat.clust.resp.suff, Unseen==FALSE)

cat.clust.resp.suff.unseen<-subset(cat.clust.resp.suff, Unseen==TRUE)

testblock.seen <- cat.clust.resp.suff.seen %>% group_by(Cond, Block, Unseen) %>% summarise(propCorrect = mean(Result), se=se(Result))

testblock.unseen <- cat.clust.resp.suff.unseen %>% group_by(Cond, Block, Unseen) %>% summarise(propCorrect = mean(Result), se=se(Result))



plot_prop_by_block_mean.seen <- ggplot(testblock.seen, aes(x=Block-1, y=propCorrect, group=Cond, fill=Cond)) +geom_errorbar(mapping=aes(ymin=propCorrect-se, ymax=propCorrect+se), size = 0.7, width=.1, alpha=.8) + geom_line(aes(color=Cond)) + geom_point(shape=21, size = 2, stroke=1) + scale_y_continuous(limits = c(0, 1))+theme_minimal(base_size = 18)+scale_color_viridis(discrete = TRUE, option = "D", name="Grammar")+scale_fill_viridis(discrete = TRUE, option = "D", name="Grammar")+labs(y='proportion of correct responses\n', x = '\n test block')+guides(fill=guide_legend(title="condition"), color = guide_legend(title="condition"))+ scale_x_continuous(breaks=seq(0,2,1))

plot_prop_by_block_mean.seen.unseen<-plot_prop_by_block_mean.seen+ geom_errorbar(data=testblock.unseen, mapping=aes(x = Block-1, ymin=propCorrect-se, ymax=propCorrect+se), size = 0.7, width=.3, alpha=.7,position=position_dodge(0.4))+geom_point(shape=21,size=2, data=testblock.unseen, mapping=aes(x = Block-1), position=position_dodge(0.4), stroke=1, alpha = 0.7)


testblock.all<- cat.clust.resp.suff %>% group_by(Cond, Block) %>% summarise(propCorrect = mean(Result), se=se(Result))
testblock.all.raw<- cat.clust.resp.suff %>% group_by(Cond, Block,Username) %>% summarise(propCorrect = mean(Result))

cat.clust.resp.suff.3.seen<-subset(cat.clust.resp.suff, Block==3 & Unseen ==FALSE)
testblock.3.seen<- cat.clust.resp.suff.3.seen %>% group_by(Cond,Block,Unseen) %>% summarise(propCorrect = mean(Result), se=se(Result))

cat.clust.resp.suff.3<-subset(cat.clust.resp.suff, Block==3)
testblock.3<- cat.clust.resp.suff.3 %>% group_by(Cond,Block,Unseen) %>% summarise(propCorrect = mean(Result), se=se(Result))

plot_prop_by_block_mean <- ggplot(testblock.all, aes(x=Block, y=propCorrect, group=Cond, fill=Cond)) +geom_errorbar(mapping=aes(ymin=propCorrect-se, ymax=propCorrect+se), size = 0.7, width=.1, alpha=.8) + geom_line(aes(color=Cond)) + geom_point(shape=21, size = 2, stroke=1) + scale_y_continuous(limits = c(0,1))+theme_minimal(base_size = 18)+scale_color_viridis(discrete = TRUE, option = "D", name="Grammar")+scale_fill_viridis(discrete = TRUE, option = "D", name="Grammar")+labs(y='proportion of correct responses\n', x = '\n test block')+guides(fill=guide_legend(title="condition"), color = guide_legend(title="condition"))+ scale_x_continuous(breaks=seq(1,3,1))

plot_prop_by_block_mean.raw <- ggplot(testblock.all.raw, aes(x=Block, y=propCorrect))+ geom_count( aes(color=Cond,size = after_stat(n), group = Cond), position =pd, alpha=0.3)+scale_size(range = c(0,8), breaks=seq(0,30,by=5))+geom_line(data = testblock.all, mapping = aes(x=Block, y=propCorrect, group = Cond, color = Cond), position = pd)+ geom_errorbar(data= testblock.all, mapping=aes(ymin=propCorrect-se, ymax=propCorrect+se, group=Cond), position=pd, width=.8)+geom_point(shape=21,size=3, data=testblock.all, mapping=aes(y=propCorrect, x=Block, group=Cond, fill =Cond), position=pd, stroke=1) +theme_minimal(base_size = 18)+scale_color_viridis(discrete = TRUE, option = "D", name="Grammar")+scale_fill_viridis(discrete = TRUE, option = "D", name="Grammar")+labs(y='proportion of correct responses\n', x = '\n test block')+guides(fill=guide_legend(title="condition"), color = guide_legend(title="condition"))+ scale_x_continuous(breaks=seq(1,3,1))


plot_prop_by_block_mean.all.seen.unseen<-plot_prop_by_block_mean.raw+geom_point(size=2, data=testblock.3, mapping=aes(x = Block, shape = Unseen, color =Cond,fill = Cond, group = Cond), position=pd, stroke=1, alpha = 1)+scale_shape_manual(values = c(24,25))+guides( shape = guide_legend(title="novel item"))

plot_prop_by_block_mean.all.seen.unseen
```


## Accuracy as a function of the number of training trials 
```{r trainingViews, echo=FALSE, message=FALSE, warning = FALSE}

cat.clust.resp.trainingViews.raw <- cat.clust.resp.suff %>% group_by(Cond, Target.training.views, Username) %>% summarise(propCorrect = mean(Result))


cat.clust.resp.trainingViews <- cat.clust.resp.suff %>% group_by(Cond, Target.training.views) %>% summarise(propCorrect = mean(Result), se=se(Result))


plot_prop_by_trainingViews <- ggplot(cat.clust.resp.trainingViews, aes(x=factor(Target.training.views), y=propCorrect, group=Cond, fill=Cond)) +geom_errorbar(mapping=aes(ymin=propCorrect-se, ymax=propCorrect+se), size = 0.7, width=.1, alpha=.8) + geom_line(aes(color=Cond)) + geom_point(shape=21, size = 2, stroke=1) + scale_y_continuous(limits = c(0, 1))+theme_minimal(base_size = 18)+scale_color_viridis(discrete = TRUE, option = "D", name="Grammar")+scale_fill_viridis(discrete = TRUE, option = "D", name="Grammar")+labs(y='Proportion of correct responses\n', x = '\n Number of training views')+guides(fill=guide_legend(title="condition"), color = guide_legend(title="condition"))


plot_prop_by_trainingViews.raw<- ggplot(cat.clust.resp.trainingViews.raw, aes(x=factor(Target.training.views), y= propCorrect))+ geom_count( aes(color=Cond,size = after_stat(n), group = Cond), position =pd, alpha=0.3)+scale_size(range = c(0,8), breaks=seq(0,40,by=10))+geom_line(data = cat.clust.resp.trainingViews, mapping = aes(x=factor(Target.training.views), y=propCorrect, group = Cond, color = Cond), position = pd)+ geom_errorbar(data=cat.clust.resp.trainingViews , mapping=aes(ymin=propCorrect-se, ymax=propCorrect+se, group=Cond), position=pd, width=.8)+geom_point(shape=21,size=3, data=cat.clust.resp.trainingViews , mapping=aes(y=propCorrect, x=factor(Target.training.views), group=Cond, fill =Cond), position=pd, stroke=1)+theme_minimal(base_size = 18)+scale_color_viridis(discrete = TRUE, option = "D", name="Grammar")+scale_fill_viridis(discrete = TRUE, option = "D", name="Grammar")+labs(y='Proportion of correct responses\n', x = '\n Number of training views')+guides(fill=guide_legend(title="condition"), color = guide_legend(title="condition")) 


plot_prop_by_trainingViews.raw
```

# Statistical analysis

```{r function to run models, echo=FALSE}

### this function checks if the model under the path given already exists, if it does, it just opens the saved model if it doesn, it allows the model to run and saves it witht he path name given ###

run_model <- function(expr, path, reuse = TRUE) {
  path <- paste0(path, ".Rds")
  if (reuse) {
    fit <- suppressWarnings(try(readRDS(path), silent = TRUE))
  }
  if (is(fit, "try-error")) {
    fit <- eval(expr)
    saveRDS(fit, file = path)
  }
  fit
}
```

```{r model data, echo=FALSE, warning = FALSE, message=FALSE}
### aggregate all factors of interest ###
cat.clust.resp.suff$Views<-cat.clust.resp.suff$Target.training.views

cc.agr.prereg<- cat.clust.resp.suff %>% group_by(Cond, Unseen, Block, Username) %>% summarise(k = sum(Result), n=length(Result))

cc.agr <- cat.clust.resp.suff %>% group_by(Cond, Views, Block, Username) %>% summarise(k = sum(Result), n=length(Result))

cc.agr$Block <- as.numeric(cc.agr$Block)-1
cc.agr.prereg$Block <- as.numeric(cc.agr.prereg$Block)-1

cc.agr.helmert.prereg <-cc.agr.prereg
cc.agr.helmert.prereg$Cond<-fct_relevel(cc.agr.helmert.prereg $Cond, "Random","Complex","Simple")

cc.agr.helmert <-cc.agr
cc.agr.helmert$Cond<-fct_relevel(cc.agr.helmert$Cond, "Random","Complex","Simple")
```


## Reported Beta binomial model 
```{r Solomon Kurz custom beta binomial family,  echo =FALSE, warning=FALSE, message=FALSE }

### brms does not support beta binomial, so we are using the one created by Solom Kurz which is the same as the one by Paul tbh ###

beta_binomial2 <-
  custom_family(
    "beta_binomial2", dpars = c("mu", "phi"),
    links = c("logit", "log"), lb = c(NA, 0),
    type = "int", vars = "trials[n]"
  )

stan_funs <- "
  real beta_binomial2_lpmf(int y, real mu, real phi, int T) {
    return beta_binomial_lpmf(y | T, mu * phi, (1 - mu) * phi);
  }
  int beta_binomial2_rng(real mu, real phi, int T) {
    return beta_binomial_rng(T, mu * phi, (1 - mu) * phi);
  }
"

stanvars <- stanvar(scode = stan_funs, block = "functions")
```

### Priors

```{r beta binomial priors, warning = FALSE, message=FALSE}
beta_Prior <- c(
    set_prior("student_t(6, 0, 1.5)", class = "Intercept"),
    set_prior("student_t(6, 0, 1.5)", class = "b"),
    set_prior("cauchy(0, 10)", class = "sd"),
    set_prior("exponential(1)", class = "phi")
)

```


### Model
```{r model beta binomial,  warning=FALSE, message=FALSE }
### repeated: establish herlmet contrast for categorical factors
options(contrasts = c("contr.helmert", "contr.poly"))

### run model if it is not already saved, if it is saved, just open the saved model under the path given as the last argument to the run_model() function. In this case it should be saved in the same directory to avoid re-running it, it takes a while. 

model.catclust.views.helmert.beta<- run_model(
        brm(formula = k | trials(n) ~ Cond + Views + Block + (Cond:Views) + (Cond:Block) + (1+Views+Block|Username),
             data=cc.agr.helmert,
             family = beta_binomial2,
             prior = beta_Prior,
             sample_prior = TRUE,
             warmup = 1000,
             iter = 4000,
             control = list(adapt_delta = 0.95),
             init_r = 0.1,
             chains = 4,
             cores= 4,
             seed = 11,
             stanvars = stanvars, 
             save_all_pars =TRUE),
        paste0(getwd(),"/model.catclust.views.helmert.beta"))
```

```{r  beta binomial plot, echo=FALSE,  warning=FALSE, message=FALSE }

### I am creating some custom plots in this block to show the histogram with the overlapped point estimates and the credible intervals ###

lower.ci.catclust.beta<-data.frame(Parameter=c("Intercept", "Complex vs Random",  "Simple vs Complex & Random", "Views", "Block", "Views (Complex vs Random)",  "Views (Simple vs Complex & Random)",  "Block (Complex vs Random)", "Block (Simple vs Complex & Random)"), ci = c(as.numeric(summary(model.catclust.views.helmert.beta)$fixed[,3])))

upper.ci.catclust.beta<-data.frame(Parameter=c("Intercept", "Complex vs Random",  "Simple vs Complex & Random", "Views", "Block", "Views (Complex vs Random)",  "Views (Simple vs Complex & Random)",  "Block (Complex vs Random)", "Block (Simple vs Complex & Random)"), ci = c(as.numeric(summary(model.catclust.views.helmert.beta)$fixed[,4])))

estimates.catclust.beta<-data.frame(Parameter=c("Intercept", "Complex vs Random",  "Simple vs Complex & Random", "Views", "Block", "Views (Complex vs Random)",  "Views (Simple vs Complex & Random)",  "Block (Complex vs Random)", "Block (Simple vs Complex & Random)"), est = c(as.numeric(summary(model.catclust.views.helmert.beta)$fixed[,1])))

plot.catclust.model.fixed <-stanplot(model.catclust.views.helmert.beta, type = "hist", pars = "^b.*")+geom_vline(xintercept = 0, color = "darkorange2", size = 0.7, alpha = 0.8)+theme_bw()+ theme(strip.background = element_blank())+geom_vline(data=lower.ci.catclust.beta,aes(xintercept=ci),  linetype='dashed',size=0.7,alpha=0.3)+geom_vline(data=upper.ci.catclust.beta,aes(xintercept=ci), linetype='dashed',size=0.7,alpha=0.3)+geom_vline(data=estimates.catclust.beta,aes(xintercept=est), size=0.7,alpha=0.6)

plot.catclust.model.fixed$data$Parameter<-recode_factor(plot.catclust.model.fixed$data$Parameter, "b_Intercept" = "Intercept", "b_Cond1" = "Complex vs Random", "b_Cond2" = "Simple vs Complex & Random", "b_Views" = "Views", "b_Block"="Block", "b_Cond1:Views" = "Views (Complex vs Random)", "b_Cond2:Views" = "Views (Simple vs Complex & Random)", "b_Cond1:Block" = "Block (Complex vs Random)", "b_Cond2:Block" = "Block (Simple vs Complex & Random)")
```


```{r bayesian model diagnostics beta requirements,  echo=FALSE,  warning=FALSE, message=FALSE}
# This is code setting the functions and ground to run the model diagnostics

### we need this to make be able to run the functions to diagnose the model. This is a built in fucntion in brms which exports user-defined Stan functions form the model and optionally vectorizes them ###
expose_functions(model.catclust.views.helmert.beta, vectorize = TRUE)

### custom functions to run beta mdoel diagnostics ###
log_lik_beta_binomial2 <- function(i, draws) {
mu <- draws$dpars$mu[, i]
phi <- draws$dpars$phi
trials <- draws$data$trials[i]
y <- draws$data$Y[i]
beta_binomial2_lpmf(y, mu, phi, trials)
}

predict_beta_binomial2 <- function(i, draws, ...) {
mu <- draws$dpars$mu[, i]
phi <- draws$dpars$phi
trials <- draws$data$trials[i]
beta_binomial2_rng(mu, phi, trials)
}

fitted_beta_binomial2 <- function(draws) {
mu <- draws$dpars$mu
trials <- draws$data$trials
trials <- matrix(trials, nrow = nrow(mu), ncol = ncol(mu), byrow = TRUE)
mu * trials
}
```


```{r bayesian model diagnostics beta,  echo=FALSE,  warning=FALSE, message=FALSE}
### This is code to run several diagnostics for the model

### set colors for the plot ###
viridis_3_rev<-c("#440154FF", "#1F968BFF", "#FDE725FF")

### evidence for hypotheses (one sided), i.e., we report posterior probabilities and their CIs when necessary. The posterior probabilities are the percentage of samples of the posterior in accordance with the hypothesis ###
ht<-hypothesis(model.catclust.views.helmert.beta, c("Cond1 > 0", "Cond2 > 0", "Views > 0", "Cond1:Views > 0", "Cond2:Views > 0", "Block < 0", "Cond1:Block < 0", "Cond2:Block > 0"))


### predictive check: a good model fit would have the thick line y within the simulated samples yrep ###
plot.pp.catclust.beta<-pp_check(model.catclust.views.helmert.beta, nsamples =  1e3, type = "bars")+theme_minimal(base_size = 18)+labs(y="Frequency \n", x ="\n Number of correct responses \n(subset by block and number of training views)")

### plot showing the fits of the point estimates and CIs for the fixed effects ###
ma.catclust.beta<-marginal_effects(model.catclust.views.helmert.beta, new_objects = list(trials = 1))

### plot of cond*Views model fit ###
pred.fit.Views.beta<-plot(ma.catclust.beta, plot = FALSE)[[4]]+theme_bw()+scale_color_viridis(discrete = TRUE, option = "D",direction = -1)+scale_fill_viridis(discrete = TRUE, option = "D", direction = -1)+theme_minimal(base_size = 18)

fit.mod.fixeff.viz.Views<-ggarrange(plot_prop_by_trainingViews.raw+labs(y="proportion of correct responses \n",  x ="", title = "Experimental results" )+theme( plot.title=element_text(size=14)),pred.fit.Views.beta+ylim(0,1)+theme(legend.position = "none", plot.title=element_text(size=14))+labs(y="",  x ="", title = "Model fit" ), legend = "right", common.legend = TRUE, widths = c(1.1,1))

combo.results.views<-annotate_figure(fit.mod.fixeff.viz.Views, bottom = text_grob("\n number of training views \n", size = 18, hjust = 0.6, vjust= -0.1))

### plot of cond*Block model fit ###
pred.fit.Block.beta<-plot(ma.catclust.beta, plot = FALSE)[[5]]+theme_bw()+scale_color_viridis(discrete = TRUE, option = "D",direction = -1)+scale_fill_viridis(discrete = TRUE, option = "D", direction = -1)+theme_minimal(base_size = 18)+ scale_x_continuous(breaks=seq(0,2,1),labels = c("1","2","3"))

### plot combining empirical data with model fit ###
fit.mod.fixeff.viz.Block<-ggarrange(plot_prop_by_block_mean.all.seen.unseen+labs(y="proportion of correct responses \n",  x ="", title = "Experimental results" )+theme( plot.title=element_text(size=14)),pred.fit.Block.beta+ylim(0,1)+theme(legend.position = "none", plot.title=element_text(size=14))+labs(y="",  x ="", title = "Model fit" ), legend = "right", common.legend = TRUE, widths = c(1.1,1))

combo.results.block<-annotate_figure(fit.mod.fixeff.viz.Block, bottom = text_grob("\n block \n", size = 18, hjust = 0.6, vjust= -0.1))

### PSIS diagnostic plot with reloo (Pareto Values will be below .7 if all is fine, otherwise it cannot be used reliably for model comparision). ### the function ran is loo(model, reloo = TRUE)
loo.views.beta.reloo<-readRDS(file=paste0(getwd(),"/loo.catclust.beta.reloo.Rds"))

### PSIS diagnostic plot as above but without the reloo ###
loo.views.beta<-readRDS(file=paste0(getwd(),"/loo.catclust.beta.Rds"))

### below some variables to chek the fit comapring PIT to a uniform distribution, again, a good fit has the thick line within the sampled light blue lines. If the thick line is very skewed towards the cieling it might reflect overdispersion. It takes a bit to run so I saved the plot object, but can be run useing the commented out lines. ###

# yrep.catclust<-posterior_predict(model.catclust.views.helmert.beta)
# y.catclust <- cc.agr.helmert$k
# psis.catclust <- loo.views.beta$psis_object
# lw.catclust <- weights(psis.catclust)
# marginal.predictive.check.catclust.beta<-ppc_loo_pit_overlay(y.catclust, yrep.catclust, lw = lw.catclust, sample = 1e3)
marginal.predictive.check.catclust.beta<-readRDS(file=paste0(getwd(),"/marginal.predictive.check.catclust.beta.Rds"))
```

### Results

#### Posterior distribution densities for fixed effects
```{r plot estimates beta,echo=FALSE,  warning=FALSE, message=FALSE}
plot.catclust.model.fixed
```

#### One-sided hypotheses for fixed effects
```{r hypotheses beta,echo=FALSE,  warning=FALSE, message=FALSE}
ht
```

#### Plots of experimental data and their respective model fits (by View and by Block)
```{r plot results and model prediction beta, echo=FALSE,  warning=FALSE, message=FALSE, fig.height=6, fig.width=10,fig.cap=""}
combo.results.views
combo.results.block
```

### Model diagnostics
```{r plot model deiagnostics beta, echo=FALSE,  warning=FALSE, message=FALSE}
plot.pp.catclust.beta
plot(loo.views.beta.reloo)#+abline(h = 0.7, col = "brown3", lty =2)
```


## Preregistered binomial model

An anonymised version of the pre-registered design and analysis plan is accessible at https://aspredicted.org/blind.php?x=a5jn8q. 

### Priors

```{r binomial priors, warning = FALSE, message=FALSE}
Prior <- c(
    set_prior("student_t(6, 0, 1.5)", class = "Intercept"),
    set_prior("student_t(6, 0, 1.5)", class = "b"),
    set_prior("cauchy(0, 10)", class = "sd")
)

```

### Model
```{r preregistered model binomial with priors,  warning = FALSE, message=FALSE}
### establish herlmet contrast for categorical factors
options(contrasts = c("contr.helmert", "contr.poly"))

### run model if it is not already saved, if it is saved, just open the saved model under the path given as the last argument to the run_model() function. In this case it should be saved in the same directory to avoid re-running it, it takes a while. 
model.catclust.binomial.prereg.helmert<- run_model(
        brm(formula = k | trials(n) ~ Cond + Unseen + Block + Cond:Unseen + Cond:Block + (1 + Unseen + Block | Username),
             data=cc.agr.helmert.prereg,
             family = binomial,
             prior = Prior,
             sample_prior = TRUE,
             warmup = 1000,
             iter = 4000,
             chains = 4,
             inits= "0",
             cores=4,
             seed = 123,
             save_all_pars =TRUE),
        paste0(getwd(),"/model.catclust.binomial.prereg.helmert"))

```

### Results

#### Posterior distribution densities for fixed effects

```{r  preregistered binomial plot, echo=FALSE,  warning=FALSE, message=FALSE }

### I am creating some custom plots in this block to show the histogram with the overlapped point estimates and the credible intervals ###

lower.ci.catclust.prereg<-data.frame(Parameter=c("Intercept", "Complex vs Random",  "Simple vs Complex & Random", "Unseen vs Seen", "Block", "Unseen vs Seen (Complex vs Random)",  "Unseen vs Seen (Simple vs Complex & Random)",  "Block (Complex vs Random)", "Block (Simple vs Complex & Random)"), ci = c(as.numeric(summary(model.catclust.binomial.prereg.helmert)$fixed[,3])))

upper.ci.catclust.prereg<-data.frame(Parameter=c("Intercept", "Complex vs Random",  "Simple vs Complex & Random", "Unseen vs Seen", "Block", "Unseen vs Seen (Complex vs Random)",  "Unseen vs Seen (Simple vs Complex & Random)",  "Block (Complex vs Random)", "Block (Simple vs Complex & Random)"), ci = c(as.numeric(summary(model.catclust.binomial.prereg.helmert)$fixed[,4])))

estimates.catclust.prereg<-data.frame(Parameter=c("Intercept", "Complex vs Random",  "Simple vs Complex & Random", "Unseen vs Seen", "Block", "Unseen vs Seen (Complex vs Random)",  "Unseen vs Seen (Simple vs Complex & Random)",  "Block (Complex vs Random)", "Block (Simple vs Complex & Random)"), est = c(as.numeric(summary(model.catclust.binomial.prereg.helmert)$fixed[,1])))

plot.catclust.model.fixed.prereg <-stanplot(model.catclust.binomial.prereg.helmert, type = "hist", pars = "^b.*")+geom_vline(xintercept = 0, color = "darkorange2", size = 0.7, alpha = 0.8)+theme_bw()+ theme(strip.background = element_blank())+geom_vline(data=lower.ci.catclust.prereg,aes(xintercept=ci),  linetype='dashed',size=0.7,alpha=0.3)+geom_vline(data=upper.ci.catclust.prereg,aes(xintercept=ci), linetype='dashed',size=0.7,alpha=0.3)+geom_vline(data=estimates.catclust.prereg,aes(xintercept=est), size=0.7,alpha=0.6)

plot.catclust.model.fixed.prereg$data$Parameter<-recode_factor(plot.catclust.model.fixed.prereg$data$Parameter, "b_Intercept" = "Intercept", "b_Cond1" = "Complex vs Random", "b_Cond2" = "Simple vs Complex & Random", "b_Unseen1" = "Unseen vs Seen", "b_Block"="Block", "b_Cond1:Unseen1" = "Unseen vs Seen (Complex vs Random)", "b_Cond2:Unseen1" = "Unseen vs Seen (Simple vs Complex & Random)", "b_Cond1:Block" = "Block (Complex vs Random)", "b_Cond2:Block" = "Block (Simple vs Complex & Random)")

plot.catclust.model.fixed.prereg
```


